---
title: "Showcase"
author: "Misha Balyasin"
date: "March 27, 2018"
output: 
  ioslides_presentation:
    smaller: true
    widescreen: true

---

## Motivation
- Way too many options
- Don't really care about cars
- Finding a car that will depreciate the least

## Source of data
- ~19k ads from around Berlin from mobile.de
- mobile.de has API if you are planning to get more data
- Detailed steps are available here https://www.mishabalyasin.com/2017/07/09/buy-car-part1/

## Couple of noteworthy things
- Way too easy
- Only takes 40 minutes to scrape
- "Inspect" tool works just fine
- Meat of the process is just
```{r eval = FALSE}
cars_df <- map_df(1:nrow(cars_id), possibly(extract_data, dummy_df))
```
- Most of the time spent finding element's ID

## Couple of graphs
```{r eval = TRUE, echo = FALSE, warning=FALSE, message=FALSE, fig.height=6}
library(tidyverse)
library(plotly)
library(skimr)

df <- readRDS( "./Data/interim/after_cleaning.Rds") %>%
  tibble::as_tibble() %>%
  dplyr::mutate(age = difftime(time1 = as.Date("2016-10-02"), fr, units = "days") %>% as.numeric)

ggplot(data = df, aes(carmake, log(price))) + geom_boxplot() + coord_flip()

```

## Couple of graphs (2)
```{r eval=TRUE, echo=FALSE}
ggplot(data = df, aes(category1, log(price))) +
  geom_boxplot() +
  coord_flip() +
  theme(axis.title.y = element_blank())

```


## Price as a function of age
```{r echo=FALSE, eval = TRUE, message=FALSE, warning=FALSE}
carmakers <- df %>% select(carmake) %>%
  group_by(carmake) %>%
  tally() %>%
  filter(n > 100)
p <- df %>%
  filter(carmake %in% carmakers$carmake) %>%
  filter(category1 == "Kleinwagen") %>%
  ggplot(data = ., aes(age, price, color = carmake)) +
    geom_point() +
    geom_smooth(se=FALSE)
ggplotly(p)

```

## Modeling

Now that we see that there is a relationship between variables, next step is to model the relationship between multiple variables.

Approach I'm taking here is an exploratory. My main motivation is not to build a perfect model, but to apply "split-apply-combine" strategy to see whether there are patterns worth exploring further. Since this is mostly a showcase, I'll be a little bit more careless while working with data, e.g., dropping columns that might have useful information, but would take too long to work with.

I'll also start with building models for each of the carmake individually to see whether predicting price makes sense. 

## Cleaning (1/2)

Dropping extra columns that are free text and/or can't be used in modeling directly.

```{r, message=FALSE}
df_mdl <- df %>%
  dplyr::select(-id, -title, -envir, -category2, -hu, -extra, -fr) %>%
  dplyr::mutate(co2_sticker = as.factor(co2_sticker)) %>%
  dplyr::filter(complete.cases(.))
carmakers <- df_mdl %>% 
  dplyr::select(carmake) %>%
  dplyr::group_by(carmake) %>%
  dplyr::tally() %>%
  dplyr::filter(n > 100)
df_mdl <- df_mdl %>%
  dplyr::filter(carmake %in% carmakers$carmake)
```

## Cleaning (2/2)
Using `skimr::skim`, I've found that `co2_sticker`, `seats` and `doors` have dominant values, so they are unlikely to have good predictive power. For that reason I drop them from analysis

`fuel_` variables and `co2_em` have implicit missing variables that are coded as 999. I convert them to explicit `NA`'s

```{r}
#skimr::skim(df_mdl)
df_mdl <- df_mdl %>%
  dplyr::select(-co2_sticker, -doors, -fuel_type) %>%
  dplyr::mutate_at(vars(starts_with("fuel_"), "co2_em"), ~dplyr::na_if(.x, 999)) %>%
  dplyr::filter(!is.na(fuel_cons_comb))
#skimr::skim(df_mdl)
```

## Splitting into groups
```{r}
make_model <- function(df) {
  lm(price ~ ., data = df)
}
nested <- df_mdl %>%
  dplyr::group_by(carmake) %>%
  tidyr::nest() %>%
  dplyr::mutate(model = purrr::map(data, make_model))
```

## Models quality
```{r, echo=FALSE}
glance <- nested %>%
  dplyr::mutate(glance = purrr::map(model, broom::glance)) %>%
  tidyr::unnest(glance, .drop = TRUE)
ggplot(glance, aes(x = adj.r.squared, y = df.residual)) +
  geom_point()
```


## Visualizing residiuals
```{r, echo = FALSE, message = FALSE}
resids <- nested %>%
  dplyr::mutate(preds = purrr::map2(data, model, modelr::add_predictions)) %>%
  tidyr::unnest(preds) %>%
  dplyr::mutate(resid = price-pred)
ggplot(resids, aes(x = age, y = resid, color = carmake)) +
  geom_line()
```

## Residuals per category
```{r, echo =FALSE, message = FALSE}
p <- ggplot(resids, aes(x = age, y = resid, color = carmake)) +
  geom_line() +
  facet_wrap(~category1, scales = "free")
ggplotly(p)
```

## Value of age
```{r, echo = FALSE}
predictors <- nested %>%
  dplyr::mutate(tidies = purrr::map(model, broom::tidy)) %>%
  tidyr::unnest(tidies)
predictors %>% dplyr::filter(term == "age") %>%
  dplyr::mutate_if(is.numeric, ~round(.x, digits = 2)) %>%
  DT::datatable()
```

## Final model
```{r, message=FALSE}
library(caret)
set.seed(42)
split <- caret::createDataPartition(df_mdl$price, p = 0.8, list = FALSE)
train <- df_mdl[split,]
test <- df_mdl[-split,]
mdl <- ranger::ranger(formula = price ~ ., data = train, importance = "impurity")
mdl
```

## Test predictions
```{r, echo = FALSE, fig.width = 10, fig.height=6}
pred <- predict(mdl, data = test)
resids <- test %>%
  dplyr::mutate(pred = pred$predictions) %>%
  dplyr::mutate(resid = price - pred)
ggplot(resids, aes(x = log(price), y = resid, color = carmake)) +
  geom_line() +
  facet_wrap(~carmake, ncol = 4, scales = "free")
```

## Variable importance
```{r, echo = FALSE}
mdl$variable.importance %>% 
  enframe %>% 
  dplyr::arrange(value) %>%
  dplyr::mutate(value = value/max(value)) %>%
  ggplot(., aes(x = reorder(name, value), y = value)) + 
    geom_bar(stat = "identity") +
    coord_flip()
```

## Conclusion

In the end we've decided not to buy car after all, but current analysis showed some interesting things that I haven't considered before

Thanks for attention, I'd be glad to answer your questions!
